introduction

### 2019-03-15 introduction.Rmd
added chunk of modelling explanation to intro. needs to be edited.

Joining aggregate socio-demographics information from the Census with federal election voting data is problematic, as there in an inherent asynchronicity in the two events - a Census occurs every five years, whereas an election usually occurs every three years. The predominant approach in previous studies is to join voting outcomes to the nearest Census, without accounting for any temporal differences (see @DavisStimson98, @Stimson06, @Liao09 and @Stimson09). Furthermore, electoral boundaries change regularly, so spatial discrepencies also arise when matching electoral data. To obtain appropriate Census data for the 2004, 2007, 2010 and 2013 elections, we adopt impute electoral socio-demographics using spatio-temporal imputation that combines areal interpolation [@Goodchild1993] and linear time-interpolation. The process of collection and wrangling is detailed in @CHAPTER2 and imputation process is outlined in @CHAPTER3.

Previous work on modelling voting outcomes with aggregate socio-demographics find that relatively good models can be fit. @Forrest01 does this using multiple regression of the Liberal and Labor primary vote for polling booths in the Farrer electorate in 1998. @Stimson06, @Stimson09 and @Stimson12 conduct principal component analysis of polling booths in the 2001, 2004 and 2007 elections respectively, also finding that socio-demographic characteristics of polling booths are linked to their two-party preferred vote. @Stimson09 also model the polling booth swing vote (change in the two-party preferred vote) in the 2007 election, but had little success. Instead of analyzing a single election in isolation, this paper employs a consistent model framework across elections so that any temporal changes are observed.

>>>>

Joining aggregate socio-demographics information from the Census with federal election voting data is problematic, as there in an inherent asynchronicity in the two events - a Census occurs every five years, whereas an election usually occurs every three years. The predominant approach in previous studies is to join voting outcomes to the nearest Census, without accounting for any temporal differences (see @DavisStimson98, @Stimson06, @Liao09 and @Stimson09). Furthermore, electoral boundaries change regularly, so spatial discrepencies also arise when matching electoral data. To obtain appropriate Census data for the 2004, 2007, 2010 and 2013 elections, we adopt impute electoral socio-demographics using spatio-temporal imputation that combines areal interpolation [@Goodchild1993] and linear time-interpolation. The process of collection and wrangling is detailed in @CHAPTER2 and imputation process is outlined in @CHAPTER3. All data and documentation involved in this study is reproducible and availabe in the `eechidna` `R` package on `CRAN`.

Previous work on modelling voting outcomes with aggregate socio-demographics find that relatively good models can be fit. @Forrest01 does this using multiple regression of the Liberal and Labor primary vote for polling booths in the Farrer electorate in 1998. @Stimson06, @Stimson09 and @Stimson12 conduct principal component analysis of polling booths in the 2001, 2004 and 2007 elections respectively, also finding that socio-demographic characteristics of polling booths are linked to their two-party preferred vote. @Stimson09 also model the polling booth swing vote (change in the two-party preferred vote) in the 2007 election, but had little success. Instead of analyzing a single election in isolation, this paper employs a consistent model framework across elections so that any temporal changes are observed. This process is discussed in @CHAPTER4 and involves standardizing variables across years, using principal components to group variables, and then selecting variables with an information-theoretic approach that uses Akaike weights to determine relative variable importance [@BurnhamAnderson2002]. Spatial error models are then fit to account for spatial dependence.

---------
